---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AnalyseR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

L'objectif de l'application est de pouvoir comparer différents packages de visualisations graphiques tels que `ggplot2` et `plotly`.

## Installation

Vous pouvez installer ce package de la façon suivante:

``` {r,eval = FALSE}
devtools::install_github("yanismicha/AnalyseR")
```

## Example


```{r example,message=FALSE}
library(AnalyseR)
library(compar)

```



You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.


```{r pressure, echo = FALSE}

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
